---
title: "p8105_hw1_acm2268"
author: "Amanda Miles"
date: "9/29/2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

#Question 1

##Creating a Data Frame

```{r problem 1 df}

set.seed(50)

p1_df = tibble(
  r_sample = rnorm(10),
  pos_vec = r_sample > 0,
  char_vec = c("sara", "steven", "kathryn", "diane", "doug", "anne", "vanessa", "justin", "kaitlyn", "jack"),
  fact_vec = factor(c("blonde","brunette", "brunette", "black", "brunette", "blonde", "brunette", "black", "blonde", "blonde" ))
)

p1_df

```

#Taking the mean

```{r problem 1 means}

r_sample_mean = mean(pull(p1_df, r_sample))
pos_vec_mean = mean(pull(p1_df, pos_vec))
char_vec_mean = mean(pull(p1_df, char_vec))
fact_vec_mean = mean(pull(p1_df, fact_vec))

r_sample_mean
pos_vec_mean
char_vec_mean
fact_vec_mean

```

I was able to take the mean of the random sample of size 10 (r_Sample), which had a mean of -0.2440498. I was also able to take the mean of the logical vector indicating whether elements of the sample are greater than 0 (pos_vec), which was 0.5. However, I was unable to take the mean of the character vector or the factor vector. This makes sense since these two variables are not numeric so we cannot take their mean.

