---
title: "p8105_hw1_acm2268"
author: "Amanda Miles"
date: "9/29/2021"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

#Question 1

##Creating a Data Frame

```{r problem 1 df}

set.seed(50)

p1_df = tibble(
  r_sample = rnorm(10),
  pos_vec = r_sample > 0,
  char_vec = c("sara", "steven", "kathryn", "diane", "doug", "anne", "vanessa", "justin", "kaitlyn", "jack"),
  fact_vec = factor(c("blonde","brunette", "brunette", "black", "brunette", "blonde", "brunette", "black", "blonde", "blonde" ))
)

p1_df

```

#Taking the mean

```{r problem 1 means}

r_sample_mean = mean(pull(p1_df, r_sample))
pos_vec_mean = mean(pull(p1_df, pos_vec))
char_vec_mean = mean(pull(p1_df, char_vec))
fact_vec_mean = mean(pull(p1_df, fact_vec))

r_sample_mean
pos_vec_mean
char_vec_mean
fact_vec_mean

```

I was able to take the mean of the random sample of size 10 (r_Sample), which had a mean of -0.2440498. I was also able to take the mean of the logical vector indicating whether elements of the sample are greater than 0 (pos_vec), which was 0.5. However, I was unable to take the mean of the character vector or the factor vector. This makes sense since these two variables are not numeric so we cannot take their mean.

#Converting variables to numeric

```{r converting variables}

as.numeric(pull(p1_df, r_sample))
as.numeric(pull(p1_df, pos_vec))
as.numeric(pull(p1_df, char_vec))
as.numeric(pull(p1_df, fact_vec))

```

#Question 2

##Load dataset

```{r load dataset}

data("penguins", package = "palmerpenguins")

```

##Describe dataset

```{r describe dataset}

skimr::skim(penguins)

nrow(penguins)
ncol(penguins)

```

##Make scatterplot

```{r plots}

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("p8105_hw1_plot_acm2268.pdf", height = 3, width = 5)

```

The penguins dataset has 344 rows and 8 columns. It contains 8 variables, including penguin species, island, penguin sex, penguin bill length in millimeters, bill depth in millimeters, flipper length in millimeters, body mass in grams, and the year. Three of these are factor variables (species, island, sex) and five are numeric variables (bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, year). The mean flipper length is 200.92 millimeters. 